Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-21 tex/MesnardoBarba2019.tex
Add PetIBM citation et al.
Also:

* Provide contour range in caption.
* Increase width of figures.

\footnotetext{NC24r: RDMA (Remote Direct Access Memory) capable with InfiniBand network.}

@@

Thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} we ran three-dimensional CFD simulations of the flow around a gliding-snake model using our in-house research software PetIBM.
Prior to that, we ran benchmarks to confirm we would get comparable performances between a local university-managed HPC cluster (Colonial One) and a public cloud platform such as Microsoft Azure.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=7cm]{figures/osu_latency_bandwidth.pdf}
    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One and on NC24r instances of Microsoft Azure.}
    \label{fig:osu_benchmarks}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=7cm]{figures/poisson_time_vs_nodes.pdf}
    \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.}
    \label{fig:poisson_benchmarks}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=7cm]{figures/wz_multi_contourf.png}
    \caption{Filled contour of the vorticity field after $20$, $44$, $45$, and $80$ time units of flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$. Vortex merging events are responsible for the change in the wake signature and the drop in the mean value of the lift coefficient.}
    \label{fig:wz_2d}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=7cm]{figures/wz_avg_multi_contourf.png}
    \caption{Filled contour of the spanwise-averaged z-component of the vorticity field after $80$ and $100$ time units of flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
    \label{fig:wz_avg_3d}
\end{figure}

@@

>>>>

\footnotetext{NC24r instances are RDMA (Remote Direct Access Memory) capable with InfiniBand network.}

@@

Thanks to a sponsorship ($\$20,000$ worth of cloud credits) from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} we ran three-dimensional CFD simulations of the flow around a gliding-snake model using our in-house research software PetIBM\cite{chuang_et_al_2018}.
Prior to that, we ran benchmarks to confirm we would get comparable performances between a local university-managed HPC cluster (Colonial One) and a public cloud platform such as Microsoft Azure.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=8cm]{figures/osu_latency_bandwidth.pdf}
    \caption{Point-to-point latency (top) and bandwidth (bottom) obtained on Colonial One and on NC24r instances of Microsoft Azure.}
    \label{fig:osu_benchmarks}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=8cm]{figures/poisson_time_vs_nodes.pdf}
    \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure.}
    \label{fig:poisson_benchmarks}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=8cm]{figures/wz_multi_contourf.png}
    \caption{Filled contour of the vorticity field ($-5 \leq w_z c / U_\infty \leq 5$) after $20$, $44$, $45$, and $80$ time units of flow simulation with PetIBM for the snake cross-section at a $35$-degree angle of attack and Reynolds number $2000$. Vortex merging events are responsible for the change in the wake signature and the drop in the mean value of the lift coefficient.}
    \label{fig:wz_2d}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=8cm]{figures/wz_avg_multi_contourf.png}
    \caption{Filled contour of the spanwise-averaged z-component of the vorticity ($-5 \leq w_z c / U_\infty \leq 5$) field after $80$ and $100$ time units of flow simulation with PetIBM for the snake cylinder with a cross-section at a $35$-degree angle of attack and Reynolds number $2000$.}
    \label{fig:wz_avg_3d}
\end{figure}

@@

\section{Cost Analysis}\label{sec:cost}
